Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-16 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
完善与其他方法的对比结果

>>>>

\subsubsection{Compared with Other Methods}

In table \ref{tab:untargeted}, we compare the untargeted attack performance of our method with CSA \cite{CSA}, FAN \cite{FAN} and TTP \cite{TTP}.
We report the precision score relative to the real trajectory on OTB2015.
Our method significantly outperforms other methods in terms of the drop rate of the precision score.

In table \ref{tab:targeted}, we compare the the targeted attck performance of our method with FAN \cite{FAN} and TTP \cite{TTP}.
Our method significantly outperforms other methods in terms of the precision score relative to the fake trajectory on OTB2015.

\begin{table}[ht]
\centering
\resizebox{0.48\textwidth}{!}{%
\begin{tabular}{@{}ccccccc@{}}
\toprule
Method & Tracker & Backbone & Attack Cost (ms) & Clean Videos & Perturbed Videos & Drop Rate \\ \midrule
CSA & SiamRPN & AlexNet & 4720 & 0.851 & 0.458 & 0.46 \\
FAN & SiamFC & AlexNet & 10 & 0.72 & 0.18 & 0.75 \\
TTP & SiamRPN++ & ResNet-50 & 8 & 0.91 & 0.08 & 0.91 \\
\midrule
Ours & SiamFC++ & GoogLeNet & 0 & 0.861 & 0.048 & 0.94 \\ \bottomrule
\end{tabular}%
}
\caption{Precision score relative to the real trajectory on OTB2015.}
\label{tab:untargeted}
\end{table}

\begin{table}[ht]
\centering
\resizebox{0.48\textwidth}{!}{%
\begin{tabular}{@{}cccc@{}}
\toprule
Method & Tracker & Backbone & Precision on Perturbed Videos \\ \midrule
FAN & SiamFC & AlexNet & 42.0 \\
TTP & SiamRPN++ & ResNet-50 & 69.2 \\
\midrule
Ours & SiamFC++ & GoogLeNet & 92.8 \\
\bottomrule
\end{tabular}%
}
\caption{Precision score relative to the fake trajectory on OTB2015.}
\label{tab:targeted}
\end{table}
